---
title: "Final_Project_Paper"
Author: "Jeffrey Gilbert"
format: html
---

The United States has been concerned about the expansion of imperial powers in the Western Hemisphere, which was exemplified by the Monroe Doctrine as well as the Corollary to the Monroe Doctrine [^fn1]: Jeffrey A. Engel, et al., America in the World: A History in Documents from the War with Spain to the War on Terror, (Princeton, NJ: Princeton University Press, 2014)23-24, 71-72. The fear of foreign influence in Latin America was especially prevalent during the interwar period and World War II. Franklin Delano Roosevelt was keenly aware of Latin America’s distaste for U.S. military intervention, so he decided to deviate from past precedence by taking the approach of being a good neighbor [^fn2]: Irwin F. Gellman, Good Neighbor Diplomacy: United States Policies in Latin America, 1933-1945, (Baltimore: Johns Hopkins University Press, 2019),11-12. Drawing from digital tools used on the Foreign Policy Bulletin Dataset, which is comprised of publications from the Foreign Policy Bulletin, the interactions driving U.S. foreign policy during Roosevelt’s presidency become more apparent. Even though Latin America’s coverage was underrepresented compared to Euro-American or Axis nations, the Foreign Policy Bulletin’s coverage of Latin America suggests that collective security efforts and hemispheric solidarity were central to U.S. foreign policy efforts. Inter-American cooperation and hemispheric solidarity were seen as essential foreign policy measures for protecting the United States from the Axis Powers. 

Over the last century, the Foreign Policy Association (FPA) has been producing content on U.S. foreign policy. Originally established as the League of Free Nations Association, the association’s initial aspirations were to support peace initiatives promulgated by Woodrow Wilson. However, the League of Free Nations Association was short-lived, and the association would shortly be changed to the FPA in 1923, where all matters of U.S. foreign policy fell under their purview of study. Moreover, the FPA had high-ranking U.S. political figures among its incorporators, including Eleanor Roosevelt and John Foster Dulles. In addition to these important incorporators, FBA members also had addresses delivered before them by Franklin D. Roosevelt [^fn3]: Foreign Policy Association, “About FPA,” accessed April 28, 2024, https://www.fpa.org/about/. In 1931, the FPA began producing the Foreign Policy Bulletin, which published articles on international events affecting U.S. foreign policy. The Foreign Policy Bulletin Dataset is comprised of the volumes produced by the Foreign Policy Bulletin between 1936 and 1946 [^fn4]: John Mark Ockerbloom, “The Online Books Page: Foreign Policy Bulletin,” accessed April 28, 2024, https://onlinebooks.library.upenn.edu/webbin/serial?id=fpabulletin. 

```{r}
#Load in Libraries
library(tidytext)
library(tidyverse)
library(readtext)
library(tm)
library(topicmodels)
library(widyr)
library(SnowballC)
library(DigitalMethodsData)
library(wordVectors)
library(magrittr)
library(dplyr)
library(ggplot2)
```

```{r}
#load in dataset
metadata <- read.csv("ForeignPolicyBulletinData/metadata.csv")

fp.metadata <- separate(metadata,
         col = date,
         into = c("year", "month", "day"),
          remove = FALSE)

fpmeta <- as.data.frame(fp.metadata)
fp_texts <- readtext(paste("ForeignPolicyBulletinData/txt/", "*.txt", sep=""))
fp_whole <- full_join(fpmeta, fp_texts, by = c("filename" = "doc_id")) %>% as_tibble() 

stop_words_custom <- stop_words %>% 
  add_row(word="foreign", lexicon="NA")%>%
  add_row(word="policy", lexicon="NA")%>%
  add_row(word="international", lexicon="NA")%>%
  add_row(word="york", lexicon="NA")%>%
  add_row(word="act", lexicon="NA")%>%
  add_row(word="bulletin", lexicon="NA")%>%
  add_row(word="3", lexicon="NA")%>%
  add_row(word="association", lexicon="NA")%>%
  add_row(word="class", lexicon="NA")%>%
  add_row(word="published", lexicon="NA")%>%
  add_row(word="2", lexicon="NA")%>%
  add_row(word="december", lexicon="NA")%>%
  add_row(word="march", lexicon="NA")%>%
  add_row(word="post", lexicon="NA")%>%
  add_row(word="vol", lexicon="NA")%>%
  add_row(word="membership", lexicon="NA")%>%
  add_row(word="incorporated", lexicon="NA")%>%
  add_row(word="weekly", lexicon="NA")%>%
  add_row(word="5", lexicon="NA")%>%
  add_row(word="1", lexicon="NA")%>%
  add_row(word="4", lexicon="NA")%>%
  add_row(word="22", lexicon="NA")%>%
  add_row(word="8", lexicon="NA")%>%
  add_row(word="6", lexicon="NA")%>%
  add_row(word="7", lexicon="NA")%>%
  add_row(word="ing", lexicon="NA")%>%
  add_row(word="de", lexicon="NA")%>%
  add_row(word="tion", lexicon="NA")%>%
  add_row(word="vera", lexicon="NA")%>%
  add_row(word="vou", lexicon="NA")%>%
  add_row(word="editor", lexicon="NA")%>%
  add_row(word="subscription", lexicon="NA")%>%
  add_row(word="page", lexicon="NA")%>%
  add_row(word="printed", lexicon="NA")%>%
  add_row(word="ment", lexicon="NA")%>%
  add_row(word="matter", lexicon="NA")%>%
  add_row(word="publications", lexicon="NA")%>%
  add_row(word="con", lexicon="NA")%>%
  add_row(word="street", lexicon="NA")

tidy_fp <- fp_whole %>%
  unnest_tokens(word, text) %>% 
  filter(str_detect(word, "[a-z']$")) %>% 
  anti_join(stop_words_custom)

tidy_fp <- tidy_fp %>% filter(!grepl('[0-9]', word))
```

The Foreign Policy Bulletin Dataset provides insights on historical foreign policy events considered significant and relevant by individuals engaging with the U.S. foreign relations community. Digital methods, particularly text analysis, reveals paradigms related to the relevance of the Latin American nations regarding U.S. foreign policy efforts during the interwar period and World War II. From counting words to using topic modeling and word vectors, text analysis has illuminated important insights on the significance of Latin America to the United States, as well as the themes and words associated most with Latin American nations. When examining the direct word references, it becomes apparent that Latin American nations were discussed far less than European nations and the Axis Powers.

```{r}
#country word count
tidy_fp_countries <- tidy_fp %>% 
  filter(word %in% c("brazil", "argentina", "germany", "britain", "japan", "mexico", "soviet", "russia", "america", "chile", "venezuela")) %>% 
  count(word, sort = TRUE)
 

tidy_fp_countries
```
In the Foreign Policy Bulletin Dataset, European nations and the Axis Powers are disproportionately focused on. In raw numbers, from 1936-1946, Britain, Germany, Russia, and Japan were directly mentioned 12,027 times. Meanwhile, Argentina, Brazil, Chile, Mexico, and Venezuela were only directly referenced 1,357 times. Yet, the bulletin’s lackluster coverage of Latin America in juxtaposition to its European counterparts should not diminish Latin America’s significance to U.S. foreign policy. The major theme associated with Latin American nations in the bulletin indicates the critical role that Latin America played in protecting U.S. interests. 

```{r}
#topic model
tidy_fp_words <- tidy_fp %>% count(filename, word)

fp.dtm <- tidy_fp_words %>% 
  count(filename, word) %>% 
  cast_dtm(filename, word, n)

fp3.lda <- LDA(fp.dtm, k = 16, control = list(seed = 12345), method = "Gibbs", alpha = 0.5)
fp3.lda

fp3.topics <- tidy(fp3.lda, matrix = "beta")

fp3.top.terms <- fp3.topics %>%
  arrange(desc(beta)) %>% 
  group_by(topic) %>% slice(1:10)

fp3.top.terms %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  scale_y_reordered()
```
With regard to the topic model output that focuses on Latin American nations, the topic model found that Argentina, Brazil, Mexico, Chile, and solidarity were co-occurring. The topic model was picked up on a major foreign policy theme that was present throughout the interwar period and World War II, which is inter-American cooperation. Since neutrality sentiment was prevalent in the United States, Roosevelt was largely unable to act outside of the Americas until the attack on Pearl Harbor. Roosevelt, instead, chose to promote inter-American solidarity to prevent the Axis Powers from penetrating into the Western Hemisphere. This inter-American cooperation manifested through Roosevelt’s Good Neighbor diplomacy, but it still had its limitations. Inter-American cooperation did not mean that Latin American nations were required to make a direct alliance with the United States; rather, it was intended to create a common bond and galvanize support for keeping out the Axis Powers from the Western Hemisphere [^fn5]: Gellman, Good Neighbor Diplomacy, 12. Indeed, word vectors further suggest this connection between solidarity and the Western Hemisphere.

```{r}
#word vectors
if (!require(wordVectors)) {
  if (!(require(devtools))) {
    install.packages("devtools")
  }
  devtools::install_github("bmschmidt/wordVectors")
}

if (!file.exists("txt")) prep_word2vec(origin="ForeignPolicyBulletinData", destination="txt", lowercase=T, bundle_ngrams=1)

if (!file.exists("corpus_vectors.bin")) {model = train_word2vec("txt","corpus_vectors.bin",vectors=200, threads=5, window=12, iter=5, negative_samples=0)} else model = read.vectors("corpus_vectors.bin")
```

```{r}
nearest_to(model,model[["argentina"]], 75)
```

```{r}
nearest_to(model,model[["solidarity"]], 75)
```

```{r}
nearest_to(model,model[["germany"]], 75)
```
The need for solidarity was tied to the fear of German expansion into Latin America. When examining the outputs of the word vector, the word vectors indicated that Argentina was co-occurring with solidarity, temporalizing, and spy. Moreover, solidarity co-occurred with hemisphere, cooperation, defense, affirming, upholding, neighborliness, neighbor, and lima. Meanwhile, Germany was co-occurring with invincible, intimidate, frighten, and injustices. In many ways, inter-American solidarity was seen as an essential barrier for keeping Germany out of Latin America and, therefore, protecting a variety of U.S. interests, ranging from national to economic security [^fn6]: Ibid., 11-12, 79-81. Under this pretext, temporalizing becomes a relevant co-occurrence as it indicates that Argentina was not directly committing itself to U.S. interests. 

U.S. politicians were skeptical about Latin Americans’ ability to defend themselves from German influence, where inter-American cooperation was the desired method for trying to reduce German influence in the region. In part, this skepticism is rooted in racist thought. U.S. officials believed that Latin Americans were vulnerable to foreign influences and helpless in staving off German expansion. They were fearful that German emigrants would infect Latin Americans by bringing fascism into the region [^fn7]: Max Paul Friedman, Nazis and Good Neighbors: The United States Campaign Against the Germans of Latin America in World War II, (New York: Cambridge University Press, 2003), 2-4. For example, Intelligence Chief, Jules Dubois, concluded that there were approximately three million individuals residing in Latin America who were potentially awaiting the Axis’ instructions to strike. This sentiment was compounded by the prolific journalist, John Gunther, who expressed that Latin Americans were complacent with German infiltration [^fn8]: Ibid., 47, 54. Furthermore, U.S. officials feared that Germany was going to use Latin America as a means to economically and militarily harm the United States. Germany had targeted deprived markets in Latin America, where they obtained favor by selling desired industrial products while purchasing Latin American goods at an increased price. The caveat was that Germany required Latin American nations to purchase these goods with a special currency, which resulted in the general decline of U.S. trade in Latin America. The decline in U.S. trade made Roosevelt uneasy, as he believed that Germany was beginning to dominate trade by wrapping “an economic fence around the United States” [^fn9]: Ibid., 86. German expansion into Latin America was also seen as a military threat to the United States. Secretary of War, Henry Stimson, theorized that Hitler would use South America as his fifth column, essentially diverting the United States attention and forces away from Europe to Latin America. Since the United States did not believe that Latin Americans were too weak to fend off foreign intervention, the United States gravitated towards hemispheric defense as a means to quell Germany’s influence [^fn10]: Ibid., 46, 54-55.

Through Good Neighbor diplomacy, the United States fostered inter-American defenses in the Western Hemisphere. For example, in 1937, the United States leased naval destroyers and sent U.S. officers to train Latin American naval forces in military tactics, where Secretary of State, Cordell Hull, indicated that the United States was providing a “neighborly service” as a ‘form of reciprocal assistance” [^fn11]: The Secretary of State to All Diplomatic Missions in the American Republics Except Brazil, Washington, August 19, 1937; Vol. V, The American Republics (1954); Foreign Relations of the United States, 1933-1945, Franklin D. Roosevelt, p. 163; HeinOnline. https://heinonline-org.libproxy.unl.edu/HOL/Page?handle=hein.forrel/frusfr0025&id=1&size=2&collection=forrel&index=forrel/frusfr, April 24, 2022. In addition to lending naval destroyers, the United States also participated in inter-American conferences. The Roosevelt administration was determined to use these conferences to foster defense pacts with Latin American nations. One of these defense pacts was the Declaration of Lima, which is in conversation with the word vector output that indicated the co-occurrences between solidarity and Lima. The Declaration of Lima had reaffirmed inter-American solidarity as well as produced an agreement for American Republics to cooperate against foreign nations who were deemed a threat in the Western Hemisphere [^fn12]: Gellman, Good Neighbor Diplomacy, 77. Another major inter-American defense pact was established at the Panama Conference. At the conference, the Under Secretary of State, Sumner Welles, secured the Declaration of Panama. This declaration expanded the United States’ presence in the region by establishing a security zone for the United States to monitor belligerent movements. In general, the declaration was well received by Latin Americans and strengthened inter-American solidarity [^fn13]: Ibid., 83-85. 

The fear of German influence in Latin America was a key factor contributing to inter-American diplomacy during the interwar period and World War II. The Roosevelt administration approached diplomacy differently in Latin America than their predecessors by fostering hemispheric solidarity through Good Neighbor diplomacy [^fn14]: Ibid., 11-12. Text analysis on the Foreign Policy Bulletin Dataset corroborates this shift in diplomatic tactics, where the Foreign Policy Bulletin’s coverage of Latin America emphasizes the ongoing efforts to foster collective security and hemispheric solidarity through inter-American cooperation. Overall, inter-American cooperation and hemispheric solidarity were seen as essential foreign policy measures for protecting the United States from the Axis Powers. 


Bibliography
Engel, Jeffrey A., Mark Atwood Lawrence, and Andrew Preston. America in the World: A History in Documents from the War with Spain to the War on Terror. Princeton, NJ: Princeton University Press, 2014.
Foreign Policy Association. “About FPA.” Accessed April 28, 2024. https://www.fpa.org/about/
Friedman, Max Paul. Nazis and Good Neighbors: The United States Campaign Against the Germans of Latin America in World War II. New York: Cambridge University Press, 2003. 
Gellman, Irwin F. Good Neighbor Diplomacy: United States Policies in Latin America, 1933-1945. Baltimore: Johns Hopkins University Press, 2019.
Ockerbloom, John Mark. “The Online Books Page: Foreign Policy Bulletin.” Accessed April 28, 2024. https://onlinebooks.library.upenn.edu/webbin/serial?id=fpabulletin
The Secretary of State to All Diplomatic Missions in the American Republics Except Brazil, Washington, August 19, 1937; Vol. V, The American Republics (1954); Foreign Relations of the United States, 1933-1945, Franklin D. Roosevelt, pp. 162-164; HeinOnline. https://heinonline-org.libproxy.unl.edu/HOL/Page?handle=hein.forrel/frusfr0025&id=1&size=2&collection=forrel&index=forrel/frusfr, April 24, 2022.
